---
title: "NOAA Toolkit"
author: "Emrick"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

#Plot with earthquake data

This package allows you to clean the data then plot the data with either timeline or map fashion.

## Clean the data

The `eq_clean_data` function provide necessary functionalities to transform the data into a form that can be plotted with ggplot2 or leafleat.

```{r, echo=FALSE}
library(noaatk)
library(ggplot2)
library(leaflet)
library(dplyr,quietly = T)
# noaa <- as.data.frame(data(noaa))
# cleaned <- eq_clean_data(noaa)
```

## Draw Timeline plot

There are 2 ggplot2 goems in the package that allow you to draw Timeline graph. One without label, while the other provide location labels.

```{r}
# plot_dat <- cleaned %>% filter(DATE< lubridate::ymd("2009-1-1") & DATE > lubridate::ymd("2005-1-1")) %>% filter(COUNTRY %in% c("CHINA", "JAPAN", "USA"))
ggplot(plot_dat, aes(x = DATE))+ geom_timeline(aes(fill = DEATHS, size = EQ_MAG_MS)) + theme_bw()
```
```{r}
ggplot(plot_dat, aes(x = DATE,y = COUNTRY))+ geom_timelinelabel(aes(fill = DEATHS, size = EQ_MAG_MS, loc = LOCATION_NAME_)) + theme_bw()
```

## Draw Map with earthquke annotations

`eq_map` function allow you to use the power of leaflet to produce an interactive map with earthquakes ploted at their 'quake-location'. There is also a very useful helper function `eq_create_label` that can be used to generate labels. 

```{r}
map_dat <- plot_dat %>% filter(COUNTRY == "CHINA")
labeled_map_dat <- map_dat %>% mutate(pop_text = eq_create_label(.))
labeled_map_dat %>% eq_map(DATE)
```

```{r}
labeled_map_dat <- map_dat %>% mutate(pop_text = eq_create_label(.))
```


